Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-07 paper/galsize_paper.tex
Commented out now-obselete paragraph in broader implications section

The broad features of the $\wproj(\rproj)$ measurements shown in Figure \ref{fig:colorclustering} give insight into the characteristics that should be exhibited by any model for the relationship between $B/T$ and $\rhalf.$ First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite. These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.

>>>>

%The broad features of the $\wproj(\rproj)$ measurements shown in Figure \ref{fig:colorclustering} give insight into the characteristics that should be exhibited by any model for the relationship between $B/T$ and $\rhalf.$ First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite. These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.
